Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-06 manuscript/manuscript.tex
Added algorithm summary in manuscript

>>>>

\subsection{Algorithm summary}

When computing any gravity field generated by an arbitrary tesseroid on a specific computation point, the new software:

\begin{enumerate}
    \item Applies the density-based discretization algorithm in case of variable density producing subdivisions of the original tesseroid,
    \item Applies the modified adaptive discretization algorithm for each subdivision, generating a set of smaller tesseroids,
    \item Computes the desired gravity field for every small tesseroid through the GLQ approximation (equation \ref{eq:glq-var-dens}).
\end{enumerate}

This steps are applied for each computation point, adding the contribution of each tesseroid to the resulting gravity field.
